---
title: "Testigrade"
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, echo=FALSE}
library(tidyverse)
library(rgdal)
library(readr)
library(shiny)
library(DT)
library(dygraphs)
library(xts)
library(leaflet)
```



# Goals

### David

1. world map
2. view a portion of the csv file
3. some toggling ability to select subsets of points by attributes


### Paul

1. The ability to just enter data on a line of the spreadsheet and have the map auto update
2. The ability to click on a point and have the relevant attribute data (including picture) pop up
3. The ability to query out points based on attributes like species, subspecies, etc



# Display Worldmap

```{r read map, echo=FALSE}
map <- readOGR("Countries_WGS84.shp")

map$OBJECTID <- as.numeric(map$OBJECTID)
```

```{r ui, echo=FALSE}
ui <- fluidPage(
  titlePanel(p("World Map", style = "color:#3474A7")),
  sidebarLayout(
    sidebarPanel(
      p("Made with", a("Shiny",
        href = "http://shiny.rstudio.com"
      ), "."),
      img(
        src = "imageShiny.png",
        width = "70px", height = "70px"
      )
    ),
    mainPanel(
      leafletOutput(outputId = "map")
    )
  )
)
```

```{r server, echo=FALSE}
server <- function(input, output) {

  output$map <- renderLeaflet({

    # Create leaflet
    pal <- colorBin("YlOrRd", domain = map$OBJECTID, bins = 7)

    labels <- sprintf("%s: %g", map$CNTRY_NAME, map$OBJECTID) %>%
      lapply(htmltools::HTML)

    l <- leaflet(map) %>%
      addTiles() %>%
      addPolygons(
        fillColor = ~ pal(OBJECTID),
        color = "white",
        dashArray = "3",
        fillOpacity = 0.7,
        label = labels
      ) %>%
      leaflet::addLegend(
        pal = pal, values = ~OBJECTID,
        opacity = 0.7, title = NULL
      )
  })
}
```


```{r Run App, echo=FALSE}
# run
shinyApp(ui = ui, server = server)
```









